\begin{rubric}{Interests}{
%  RESEARCH INTERESTS
%\subrubric{Research}
    \entry* \textbf{Law of accelerating returns}: All my research interests were
    in some way shaped by the vision of Ray Kurzweil about the possibilities of
    the future and his analysis of the exponential growth of technology and the
    impact of that growth on our societies and way of life. To get the feeling,
    here is a nice introductory
    \htmladdnormallink{video}{http://www.ted.com/index.php/talks/ray_kurzweil_on_how_technology_will_transform_us.html}.


%    Vou omitir esta parte, to meio que distante da Nanotech hoje em dia
%    \entry* \textbf{Nanotechnology}: I'm interested in the possibility of
%    programmable materials on the nano scale, and their possible impact on
%    everyday life. This interest was sparked by the works of Robert Freitas and
%    his excellent Nanomedicine book and by K. Eric Drexler's Engines of
%    Creation, a pretty excellent book on it. 

    \entry* \textbf{Technology\&Education}: People like 
    Seymour Papert, Alan Kay and Douglas Engelbart inspired me to
    start learning about learning and to investigate how technology can augment
    our cognitive abilities.
    
    \htmladdnormallink {Here}{http://www.cnxs.com.br/posts/new-article-on-pedagogical-development}
    is a link for the article (it's work in progress, so any review is
    appreciated). If you never heard of Papert, I urge you to check his book
    Mindstorms and take a look at some of
    \htmladdnormallink{his}{http://homepage.mac.com/stager/iMovieTheater23.html}
    \htmladdnormallink{lectures}{https://logothings.wikispaces.com/}.

    \entry* \textbf{Brain/Machine Interface\&AI}: Due to the contact with
    Papert's philosophies and also Marvin Minsky's book, The Society of the
    Mind, and watching professor \htmladdnormallink{Nicolelis}{http://www.nicolelislab.net/}
    speak.

%  PERSONAL INTERESTS
%\subrubric{Personal}
    \entry* \textbf{JiuJitsu\&Aikido}: Great ways to get in shape and to get in
        contact with your body.

    \entry* \textbf{Surf}: Another great sport, a way to restore some connection
    with nature.

    \entry* \textbf{Knowing new people and ideas}: It's the best way to keep
    your mind fresh and your beliefs in check. Plus it's a great way to broaden
    the horizons of the mind.

    \entry* \textbf{Graphic Novels}: Very communicative medium to express deep
    ideas, plus I love comics :D

    \entry* \textbf{Documentaries}: Nice way to be informed and have some
    entertainment. 

}\end{rubric}

