\begin{rubric}{Professional Experience} 
    

    \entry*[2009]% 
        \textbf{Educator and Researcher}. Helping some people develop 
        programming skills and taste, mostly using as textbooks
        \htmladdnormallink{HTDP}{http://www.htdp.org} and
        \htmladdnormallink{SICP}{http://mitpress.mit.edu/sicp/full-text/book/book.html}.
        Also I've been researching education, cognition and epistemology.

    \entry*[2009]% 
        \textbf{Contractor for
        \htmladdnormallink{DevRepublic}{http://devrepublic.nl/}}. Basically the
        default rails web 2.0 contract gig.

    \entry*[2007 - 2008]% 
        \textbf{Contractor for \htmladdnormallink{ELC}{http://www.elctech.com} a rails house} 
        developing a multitude of ``web 2.0'' services, from CMS to social networks.

    \entry*[2007]% 
        \textbf{Contractor for \htmladdnormallink{Ursa Minor}{http://ursaminor.com/} 
        in a Dupont green \htmladdnormallink{site}{http://www.liveneutraldupont.org/dupont}}.
        I was an all around developer for the site, doing stuff from the
        UI(mostly AJAX) to the background and cart functionality .

    \entry*[2007]% 
        \textbf{Developer for \htmladdnormallink{AuctionPal}{http://www.auctionpal.com/}} 
        in their internal rails Auction Expert system. Mostly controller/model area of
        the MVC stack. Unfortunately the project was discontinued.

    \entry*[2005 - 2007]% 
        \textbf{Software Developer/Interface Engineer} for 
        \htmladdnormallink{LabSEC}{http://www.labsec.ufsc.br}(UFSC's security lab) Helping
        to build a crypto library in C++ called \htmladdnormallink{libcryptosec}{http://projetos.labsec.ufsc.br/libcryptosec} 
        to facilitate the development of cryptography
        applications(openSSL is a pain, so we built a shell around it).

    \entry*[2005 - 2007]% 
        \textbf{Software Developer/Interface Engineer} in 
        \htmladdnormallink{LabSEC}{http://www.labsec.ufsc.br}(UFSC's security lab) developing a
        Digital Certificate Management System  called
        \htmladdnormallink{ywapa}{http://projetos.labsec.ufsc.br/ywapa} for the national
        Certificate Authority of the brazilian federal government.

\end{rubric}
